Associations of severe COVID-19 with polypharmacy in the REACT-SCOT case-control study (draft only, not to be quoted)

### 2020-06-15 pharmaco.Rmd
refactored to create new file drugs.R

Table \ref{tab:numdrugs.listed.any} shows that the COVID-19 was associated with polypharmacy in those without a listed condition, but that in those with a listed condition the direction of this association was reversed: those with dispensed prescriptions of 1 to 12 drug classes were at lower risk than those with no dispensed prescriptions. 
<!---
The association of COVID-19 with polypharmacy was strongest in those who had no hospital diagnoses in the previous three years (because they had not been admitted to hospital).  In this group, with the no dispensed prescriptions category as baseline, the rate ratio ranged from `r table.numdrugsgr.num.icdch[2, 4]` in those with 1 to 3 drug classes dispensed to `r table.numdrugsgr.num.icdch[6, 4]` in those with more than 12 drug classes dispensed.

Risk of COVID-19 was strongly related to polypharmacy in all age bands: with no dispensed prescriptions as baseline category, the rate ratios (95% CIs) associated with dispensing of 12 or more drug classes were `r table.numdrugsgr.agegr[6, 4]` in those aged less than 60 years, `r table.numdrugsgr.agegr[12, 4]` in those aged 60-74 years, and `r table.numdrugsgr.agegr[18, 4]` in those aged 75 years and over. 
--->

@@

>>>>

Table \ref{tab:numdrugs.listed.any} shows that the COVID-19 was associated with polypharmacy in those without a listed condition, but that in those with a listed condition the direction of this association was reversed: those with dispensed prescriptions of 1 to 12 drug classes were at lower risk than those with no dispensed prescriptions.

@@

```{r dosegr.opiate, echo=FALSE, warning=FALSE, message=FALSE}

knitr::kable(table.dosegr.opiate,
             escape=FALSE,
             label="dosegr.opiate", 
             booktabs=TRUE,
             row.names=TRUE, 
             col.names=c(clean.header(colnames(table.dosegr.opiate)[1:2]), 
                         "Rate ratio (95\\% CI)", "$p$-value",
                         "Rate ratio (95\\% CI)", "$p$-value"),
             caption="Associations of severe COVID-19 with dispensed average daily dose (MME) of opiate grouped into categoriesb") %>%
    add_header_above(c(" "=3, "Univariate"=2, "Multivariate"=2)) %>%
    kableExtra::group_rows("Average dispensed daily dose (MME) of opiates", 1, 4) %>%
        kable_styling(latex_options="hold_position") %>%
        landscape()
